---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
  orientation: columns
  vertical_layout: fill
  theme: cosmo
runtime: shiny
---
  
```{r setup, include=FALSE}
library(flexdashboard)
```

```{r}
```

Geographical Status
=========================================
  
### Frame 1 {data-commentary-width=400}
  
```{r}

```

Time Series {data-orientation=columns}
=========================================
  
Row {data-height=650}
-------------------------------------
  
### Overall situation since start
  
```{r}
```

Row {data-height=350}
-------------------------------------
  
### Confirmed Cases
  
```{r}
```   

### Recovered Cases

```{r}

```

### Expired Cases

```{r}

```

Time Series Animation {data-orientation=columns}
=========================================
  
Row {data-height=650}
-------------------------------------
  
### Animated Graph
  
```{r}

```

News from Pakistan {data-orientation=rows}
=========================================
  
Row {.tabset .tabset-fade}
-------------------------------------
  
### Under Development {data-height=3000}
  
```{r}

```

### Under Development {data-height=3000}

```{r}

```

### Under Development {data-height=3000}

```{r}

```

About us and Data {data-orientation=rows}
=========================================
  
### About Us {data-height=3000}
  
```{r}

```

Raw Data {data-orientation=rows}
=========================================
  
Row {.tabset .tabset-fade}
-------------------------------------
  
### Confirmed Cases {data-height=3000}
  
```{r}

```

### Recovered Cases {data-height=3000}

```{r}

```

### Deaths {data-height=3000}

```{r}
```

























